Union and intersection contracts are hard, actually

### 2021-07-29 paper.tex
A note on uncurrying as a work around for K&T overloading limitation

This semantics has limited support for overloading. Consider the
example in Figure~\ref{fig:intersection-distribution}: it could
evaluate to the pair \nickel{(1, 1)}. But the coinductive semantics
of this work rejects it as a contract violation.
This can be phrased pithily as the fact that the
coinductive semantics doesn't validate the property \nickel{A -> B @&
  A -> C}$\simeq$\nickel{A -> (B @& C)}.

@@

>>>>

This semantics has limited support for overloading. Consider the
example in Figure~\ref{fig:intersection-distribution}: it could
evaluate to the pair \nickel{(1, 1)}. But
\citeauthor{KeilThiemannUnionIntersection}'s coinductive semantics
rejects it as a contract violation.
This can be phrased pithily as the fact that the
coinductive semantics doesn't validate the property \nickel{A -> B @&
  A -> C}$\simeq$\nickel{A -> (B @& C)}.

@@

A solution, for the programmer, is to use an uncurried function
\nickel{fun (x, y) => x}. So one way to think about this limitation is
that currying function is not fully supported.
